---
name: Noah Giebink
# position: "Graduate Assistant"
aboutme: Aspiring Data Scientist, Scientific Researcher, Insight Communicator
address: "University of Arizona"
email: "nwgiebink@gmail.com"
github: nwgiebink
linkedin: nwgiebink
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# packages
library(vitae)
library(tibble)
library(tidyverse)
# data
education <- read_csv(file = '../data/education.csv')
teaching <- read_csv('../data/teaching.csv')
awards <- read_csv('../data/awards.csv')
coursework <- read_csv('../data/coursework.csv')
research <- read_csv('../data/research.csv')
skills <- read_csv('../data/skills.csv')
workshops <- read_csv('../data/workshops.csv')
experience <- read_csv('../data/experience.csv')
```

# Skills

```{r}
skills %>%
  filter(grepl('general', tag, ignore.case = T)) %>%
  detailed_entries(with = type, what = skill)
```

# Education

```{r}
education %>% 
  detailed_entries(what = degree, 
                   with = school, 
                   when = year, 
                   where = where)
```

# Experience

## Business Analytics
```{r}
experience %>%
  filter(tag == 'consulting') %>%
  detailed_entries(with = company, what = role, where=where, when = date, why = details)

```

## Data Science and Research
```{r}
experience %>%
  filter(tag == 'data' | tag == 'research') %>%
  detailed_entries(with = company, what = role, where=where, when = date, why = details)

```

## Communication
```{r}
experience %>%
  filter(tag == 'teaching') %>%
  detailed_entries(with = company, what = role, where=where, when = date, why = details)

```

## Agriculture
```{r}
experience %>%
  filter(tag == 'agriculture') %>%
  detailed_entries(with = company, what = role, where=where, when = date, why = details)

```

# Contributed Workshops

```{r}
workshops %>%
  filter(tag == 'contributed') %>%
  detailed_entries(with = venue, what = name, why = details, when = date)
```

# Relevant Coursework

## Programming
```{r}
coursework %>%
  filter(grepl('data', tag)) %>%
  filter(type == 'Programming') %>%
  brief_entries(what = course)
```
## Math and Statistics
```{r}
coursework %>%
  filter(grepl('data', tag)) %>%
  filter(type == 'Math and Statistics') %>%
  brief_entries(what = course)
```

# Publications
Russell, A.L., Kikuchi, D.W., **Giebink, N.W.**, & D.R. Papaj. (2020).  Sensory bias and signal detection tradeoffs maintain intersexual floral mimicry. Philosophical Transactions B special issue. 

De Luca, P. A., **Giebink, N.**, Mason, A. C., Papaj, D., & Buchmann, S. L. (2018). How well do acoustic recordings characterize properties of bee (Anthophila) floral sonication vibrations? Bioacoustics, 1–14. 



